### 2018-10-12 Manuscript/Manuscript.tex

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.65\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{\textbf{Map of current extent of lithologies associated with LIPs and estimates of the initial LIP area.}}
	\label{fig:LIP_map}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/LIP_Map_0_520.pdf}
	\caption{\textbf{Map of current extent of lithologies associated with LIPs that erupted between 520 Ma and the present (shown in orange) as well as the estimates of the initial LIP area used in the area analysis (shown in blue).}}
	\label{fig:LIP_map}
\end{center}
\end{figure}
